API design for machine learning software: experiences from the scikit-learn project

### 2013-09-28 paper.tex
cite Oliphant's CiSE article for NumPy and SciPy

\sklearn is designed to tie in with the set of numeric
and scientific packages centered around the NumPy and SciPy libraries. NumPy
\citep{vanderwalt2011} augments Python with a contiguous numeric array datatype
and fast array computing primitives,
while SciPy \citep{varoquaux2013scipy} extends it
further with common numerical operations, either by implementing
these in Python/NumPy or by wrapping existing C/C{}\verb!++!/Fortran code.
The name ``scikit'' derives from (domain-specific) ``SciPy toolkit''
and is shared with \textit{scikit-image}.\footnote{\url{http://scikit-image.org}}
IPython \citep{perez2007ipython} and Matplotlib \citep{hunter2007matplotlib}
complement SciPy to provide a \textsc{matlab}-esque working environment
suited for scientific use.

@@

\sklearn's data representation is kept as close as possible
to this matrix formulation: datasets are encoded as
two-dimensional NumPy arrays or SciPy sparse matrices,
while target vectors are ``flat'' arrays of numbers or strings.
While these may seem rather unsophisticated when
compared to more object-oriented constructs, such as the ones used by
Weka \citep{hall2009weka},
they allow us to rely on efficient NumPy and SciPy vector operations
while keeping the code ``close to the textbook.''
Given the pervasiveness of NumPy and SciPy in many other scientific Python
packages, many scientific users of Python
will already be familiar with these data structures,
and a collection of available data loading and conversion tools
facilitate interoperability.
For tasks where the inputs are text files or semi-structured
objects, we provide \textit{vectorizer} objects that efficiently convert such
data to the NumPy or SciPy formats.

>>>>

\sklearn is designed to tie in with the set of numeric
and scientific packages centered around the NumPy and SciPy libraries
\citep{oliphant2007python, vanderwalt2011}.
NumPy augments Python with a contiguous numeric array datatype
and fast array computing primitives,
while SciPy extends it further with common numerical operations,
either by implementing these in Python/NumPy
or by wrapping existing C/C{}\verb!++!/Fortran code.
The name ``scikit'' derives from ``SciPy toolkit''
and is shared with \textit{scikit-image}.\footnote{\url{http://scikit-image.org}}
IPython \citep{perez2007ipython} and Matplotlib \citep{hunter2007matplotlib}
complement SciPy to provide a \textsc{matlab}-esque working environment
suited for scientific use.

@@

\sklearn's data representation is kept as close as possible
to this matrix formulation: datasets are encoded as
two-dimensional NumPy arrays or SciPy sparse matrices \citep{vanderwalt2011},
while target vectors are ``flat'' arrays of numbers or strings.
While these may seem rather unsophisticated when
compared to more object-oriented constructs, such as the ones used by
Weka \citep{hall2009weka},
they allow us to rely on efficient NumPy and SciPy vector operations
while keeping the code ``close to the textbook.''
Given the pervasiveness of NumPy and SciPy in many other scientific Python
packages, many scientific users of Python
will already be familiar with these data structures,
and a collection of available data loading and conversion tools
facilitate interoperability.
For tasks where the inputs are text files or semi-structured
objects, we provide \textit{vectorizer} objects that efficiently convert such
data to the NumPy or SciPy formats.
